Structural Determinants of Sequence Evolution in Enzymatic proteins

### 2015-04-18 manuscript/voronoi/mnv.tex
minor revision of MN

    \subsection{Average Side-Chain Coordinates as the Best Representation of Protein 3D Structure}
    \label{sec:voronoi_SC}

@@

    \subsection{Average Side-Chain B Factors as the Best Representation of Local Fluctuations of Amino Acids in Proteins}

>>>>

    \subsection*{Average Side-Chain Coordinates as the Best Representation of Protein 3D Structure}
    \label{sec:voronoi_SC}

@@

    \subsection*{Average Side-Chain B Factors as the Best Representation of Local Fluctuations of Amino Acids in Proteins}
